Parameter estimation

### 2023-04-22 SFE-article/Sections/Experiments.tex
24.03
22.04

	The close the optimization problem given by set of equations \ref{EQ: Optimization_formulation_MLE}, it is require to know the dataset $Y(t)$. In this case, the dataset have been obtained by performing extraction of caraway oil from caraway seeds. The caraway seeds have been obtained from the company Caraway Finland\todo{Should be mentioned?} during 2022 growing season. The caraway seeds have been pre-treated with Retsch SM 300 cutting mill to decrease the particle size to 1mm and break the outer shell of the seeds. Later, the moisture content was analysed to ensure that it does not have a negative effect on the extraction process. An Infrared Moisture Analyser was used to investigate the sample. The moisture content after grinding was 4.83\%. The grind material density was measured by pyncometery and its result can be found in appendix \ref{CH: Solid_Density_Measurment}

	The unit used for the experimental work is 10 litre extractor \todo{Should Biorukki be mentioned?} with inner diameter around 15 cm and 60 cm height \todo{Double check dimension}. Four experiments have been performed in that unit at following operating conditions: $40^\circ C / 200$ bar, $50^\circ C / 200$ bar, $40^\circ C / 300$ bar and $50^\circ C / 300$ bar. 1 kg of grind material was weighted and placed in the extraction chamber. Due to some technical limitations, the amount of solid material fro extraction was selected to be 1 kg per batch, which is not sufficient to fill the whole chamber.

@@

	\begin{table}[H]

@@

@@

			5        & 2.3                     & 1.8                     & 1.1                     & 1.2                     \\
			10       & 5.9                     & 5                       & 4.7                     & 4.5                     \\
			15       & 11.4                    & 8.6                     & 10.8                    & 11.3                    \\
			20       & 17.7                    & 13.7                    & 20.6                    & 20.6                    \\
			25       & 24.4                    & 18.3                    & 32.1                    & 30.6                    \\
			30       & 30.4                    & 22.3                    & 40.5                    & 37.8                    \\
			35       & 34.1                    & 26.4                    & 46.7                    & 43.3                    \\
			40       & 37.6                    & 30.2                    & 50.5                    & 47.5                    \\
			45       & 40.2                    & 33.8                    & 53.1                    & 50.8                    \\
			50       & 43.4                    & 37.3                    & 55.5                    & 53.7                    \\
			55       & 45.6                    & 40.9                    & 57.6                    & 56.5                    \\
			60       & 47.7                    & 44.2                    & 59.3                    & 58.1                    \\
			65       & 49.3                    & 46.8                    & 60.9                    & 59.6                    \\
			70       & 50.9                    & 49.1                    & 62.2                    & 61.1                    \\
			75       & 52.7                    & 50.9                    & 63.7                    & 62.7                    \\
			80       & 54.3                    & 52.6                    & 64.9                    & 64.4                    \\
			85       & 55.2                    & 54                      & 66.6                    & 65.8                    \\
			90       & 56.3                    & 55.4                    & 67.6                    & 66.7                    \\
			95       & 57.4                    & 56.6                    & 68.9                    & 67.4                    \\
			100      & 58.4                    & 57.8                    & 69.7                    & 68.2                    \\
			105      & 59.5                    & 58.6                    & 70.6                    & 69.1                    \\
			110      & 60.4                    & 59.8                    & 71.2                    & 70.1                    \\
			115      & 61.5                    & 60.9                    & 71.9                    & 70.9                    \\
			120      & 62.6                    & 62.1                    & 72.3                    & 71.6                    \\
			125      & 63.4                    & 63                      & 72.8                    & 72.3                    \\
			130      & 64.1                    & 64.1                    & 73.2                    & 72.9                    \\
			135      & 64.9                    & 65.1                    & 73.6                    & 73.5                    \\
			140      & 65.6                    & 66                      & 74                      & 74                      \\
			145      & 66.3                    & 66.9                    & 74.3                    & 74.5                    \\
			150      & 66.9                    & 67.7                    & 74.6                    & 74.9                   
		\end{tabular}

>>>>

	The close the optimization problem given by set of equations \ref{EQ: Optimization_formulation_MLE}, it is require to know the dataset $Y(t)$. In this case, the dataset have been obtained by performing extraction of caraway oil from caraway seeds. The caraway seeds have been obtained from the company Caraway Finland\todo{Should be mentioned?} during 2022 growing season. The caraway seeds have been pre-treated with Retsch SM 300 cutting mill to decrease the particle size to 1mm and break the outer shell of the seeds. Later, the moisture content was analysed to ensure that it does not have a negative effect on the extraction process. An Infrared Moisture Analyser was used to investigate the sample. The moisture content after grinding was 4.83\%. The grind material density was measured by pyncometery and its result can be found in appendix \ref{CH: Solid_Density_Measurment}. Moreover the porosity was calculated to be 0.5, as explained in appendix \ref{CH: Porosity}.

	The unit used for the experimental work is 10 litre extractor \todo{Should Biorukki be mentioned?} with inner diameter around 15 cm and 60 cm height \todo{Double check dimension}. Four experiments have been performed in that unit at following operating conditions: $40^\circ C / 200$ bar, $50^\circ C / 200$ bar, $40^\circ C / 300$ bar and $50^\circ C / 300$ bar. 1 kg (or 1.6 litre) of grind material was weighted and placed in the extraction chamber. Due to technical limitations, the amount of solid material for extraction was selected to be 1 kg per batch, which is not sufficient to fill the whole chamber.

@@

	\begin{table}[tbh!]

@@

		\adjustbox{max width=\columnwidth}{%

@@

			5        & 1.7                     & 1.8                     & 1.1                     & 1.2                     \\
			10       & 5.7                     & 4.7                     & 4.7                     & 4.5                     \\
			15       & 10.9                    & 9.5                     & 10.8                    & 11.3                    \\
			20       & 17.8                    & 15.1                    & 20.6                    & 20.6                    \\
			25       & 24.9                    & 21.3                    & 32.1                    & 30.6                    \\
			30       & 30.3                    & 26.4                    & 40.5                    & 37.8                    \\
			35       & 34.0                    & 29.8                    & 46.7                    & 43.3                    \\
			40       & 37.5                    & 33.1                    & 50.5                    & 47.5                    \\
			45       & 40.1                    & 35.6                    & 53.1                    & 50.8                    \\
			50       & 43.3                    & 38.7                    & 55.5                    & 53.7                    \\
			55       & 45.5                    & 41.5                    & 57.6                    & 56.5                    \\
			60       & 47.6                    & 43.5                    & 59.3                    & 58.1                    \\
			65       & 49.2                    & 45.9                    & 60.9                    & 59.6                    \\
			70       & 50.8                    & 48.3                    & 62.2                    & 61.1                    \\
			75       & 52.6                    & 50.8                    & 63.7                    & 62.7                    \\
			80       & 54.2                    & 52.9                    & 64.9                    & 64.4                    \\
			85       & 55.1                    & 55.3                    & 66.6                    & 65.8                    \\
			90       & 56.2                    & 57.2                    & 67.6                    & 66.7                    \\
			95       & 57.3                    & 58.3                    & 68.9                    & 67.4                    \\
			100      & 58.3                    & 59.4                    & 69.7                    & 68.2                    \\
			105      & 59.4                    & 60.4                    & 70.6                    & 69.1                    \\
			110      & 60.2                    & 61.6                    & 71.2                    & 70.1                    \\
			115      & 61.4                    & 62.7                    & 71.9                    & 70.9                    \\
			120      & 62.5                    & 63.9                    & 72.3                    & 71.6                    \\
			125      & 63.3                    & 64.7                    & 72.8                    & 72.3                    \\
			130      & 64.0                    & 65.4                    & 73.2                    & 72.9                    \\
			135      & 64.8                    & 65.9                    & 73.6                    & 73.5                    \\
			140      & 65.5                    & 66.4                    & 74                      & 74                      \\
			145      & 66.2                    & 67.1                    & 74.3                    & 74.5                    \\
			150      & 66.8                    & 67.7                    & 74.6                    & 74.9                   
		\end{tabular} }

### 2023-04-22 SFE-article/Sections/Results.tex
22.04

>>>>

    The parameter estimation problem was solved by fitting the process model to the dataset \ref{tab: Yield_data}. Each time-series was fitted to the model separately. As a result of fitting, the following parameters were obtained:

    \begin{itemize}
        \item Partition coefficient $k_m$
        \item Internal Diffusion coefficient $D_i$
        \item Axial Diffusion coefficient $D_e^M$
        \item Standard Deviation $\sigma$
    \end{itemize}

    Moreover, the initial state estimation was performed together with parameter estimation. The concentration of solute is assumed to be constant and uniformly distributed. On the other hand, the solute concentration is assumed to not be uniform and not zero, which is common assumption. During the preparation period, when the operating conditions are achieved, the solute diffuses to the fluid phase in contact with the solid particles. Later, the solute in fluid phase is partially moved (if the pressure increase to the system the pump cause the movement of the fluid, even if the outlet valve is closed) to the region, where there is no solid phase. As a result, the distribution of solute in the fluid phase should be also estimated as it is unknown. Some conclusion can be drown from analysis of the initial part of each yield curve. It can be noticed, that each curve at the beginning has a curvature, which is not linear. In general sens, it can be said that a quadratic function could approximate initial part of each extraction curve. A function which after integration gives a quadratic-like result is a straight line. Based on that observation, the concentration of solute in fluid phase is assumed to be linearly distributed. The concentration of solute is assumed to be zero, at the outlet and reach maximum at beginning of the fixed bed. Such a formulation allows to fully describe the linear distribution of solute in the solid phase if the total mass of solute in the fluid phase is know, as explained in appendix \todo[]{Add chapter}. The total mass of solute in the fluid phase can be obtained from the total mass of solute $m_{total}$ and partition coefficient $\tau$, which is defined as

    {\footnotesize
    \begin{equation*}
        \tau = \cfrac{\text{total mass of solute in the fluid phase}}{\text{total mass of solute in the system}} = \cfrac{m^0_{fluid}}{m_{total}}
    \end{equation*}
    }

    Due to initial state estimation, two additional parameters are fitted

    \begin{itemize}
        \item Total mass of solute $m_{total}$
        \item Partition coefficient $\tau$
    \end{itemize}
